\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage{algorithm}
\usepackage{algpseudocode}

\title{Report for assignment 2}
\author{Vasudha Todi (14EC10059)}

\begin{document}

\maketitle

\paragraph{Divide and Conquer}
\begin{enumerate}
 \item \textbf{To fill an n*n board with one missing tile using L shaped tiles (n is a power of 2)}\\
The problem is solved using divide and conquer by dividing the board into 4 parts in each recursive step. One of the 4 sub-squares will contain the missing tile. An L shaped tile is placed at the center using the remaining 3 sub-squares, which then act as the missing tiles in the corresponding subproblems.

  \begin{algorithm}
    \caption{Divide and Conquer 1}
    \begin{algorithmic}[1]
    \State{Board}{$(A,n)$}
    \If{$n = 2$}                         //Base case
        \State Put an L shaped tile in the remaining 3 boxes 
        \State return
    \EndIf
    \State Determine the sub-square containing the missing tile
    \State place an L shaped tile at the center using the remaining 3 sub-squares.
    \State Recursive call to A() for each sub-square
    \State return
    \end{algorithmic}
  \end{algorithm}
  
 The tiles are displayed using different numbers.
 
 \textbf{Results :}
 
 Value of n : 4\\
 Missing tile at : (2,3)
 
 Output :\\
 \(
 \left[
 \begin{array}{cccc}
 2 & 2 & 3 & 3\\
 2 & 1 & 1 & 3\\
 4 & 1 & 5 & -1\\
 4 & 4 & 5 & 5\\
 \end{array}
 \right]
 \)
 \item \textbf{To find the closest pair out of n points}\\
The n points are divided into two parts. The closest pair is found out recursively in the two halves and the shorter of the two is taken. A strip is taken at the center to compare the points of the two parts with each other in a minimum number of steps.

 \begin{algorithm}
    \caption{Divide and Conquer 2}
    \begin{algorithmic}[1]
    \State{shortestDist}{$(A,Ax,n,start,end)$}
    \If{$(end-start)<=3$}
        \State Find the closest pair using brute force 
        \State return min
    \EndIf
    \State $mid = (start+end)/2$
    \State a = shortestDist(A,Ax,n,start,mid)
    \State b = shortestDist(A,Ax,n,mid+1,end)
    \State sd = min(a,b)
    \State Take a strip having y co-ordinates (mid-sd) to (mid+sd)
    \State Store the points in the strip in the order of their x co-ordinates(total c points)
    \For {$i = 1, c$}
        \State Check the distance between all the point in the strip within an x distance of sd from the ith point
        \If{$dist<sd$}
            \State sd = dist
        \EndIf
    \EndFor
    \State return sd
    \end{algorithmic}
  \end{algorithm}
  
  \textbf{Results :}
  
  No. of points : 4\\
  Points : (1,2), (4,5), (6,7), (10,12)
  
  Output :\\
  The closest points are (4,5) and (6,7)\\
  The shortest distance between them is : 2.828427
  
\end{enumerate}
\end{document}
